Reading Notes

### 2020-05-20 paper.tex
reading about PCE of donor molecules in BHJ

\cite{Scharber2006a}
\cite{Yu1995}
\cite{Halls1995}
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}

>>>>

\cite{Scharber2006a}
Design rules for donor in BHJ solar cells
interpenetrating network of C60 and conjugated polymer have shown ultrafast charge transfer (~40 fs). There is no competing decay process in this timeframe. optimized mixture with C60 converts absorbed photons to electrons with efficiency close to 100\%. At time of publishing best PCE is ~5\%. Efficiency is limited by low open circuit voltage of device under illumination. Organic semiconductors with bandgap of 2eV are used but observed $V_{oc}$ is in the range of 0.5-1 V. $V_{oc}$ in a metal-insulator-metal is equal to the work-function difference of the two electrodes. In polymer-fullerene $V_{oc}$ is affected by the morphology of active layer, electrochemical potential of the cathode. Ref 15 (Gadisa) studied correlation between electrochemistry andVoc of  polymer fullerene with PCBM and polythiophene and found that variation of the oxidation potential of the polymer caused variation in the photovoltage. (This is not the same as $V_{oc}$ ?) This paper suggests that Voc is related to HOMO of the polymer. and thus the maximum efficiency can be predicted.
I am confused by a lot in the paper and don't understand why Voc is the limiting factor. Fig 2 is interesting, shows how they predict PCE from HOMO/LUMO and bandgap. Should Eg (bandgap) be LUMO acceptor - HOMO donor?
OK so they don't really give suggestions for what kind of chemistry makes a better donor, but they do say that measuring the HOMO of the donor can tell a lot about the PCE of the device.

\cite{Yu1995}
\cite{Halls1995}
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
